### 2024-07-22 NN/tables/backward.tex
commit

    \begin{table*}
        \centering
        \begin{tabular}{p{12cm}r}r}
\hline
\hline
 features                                                                                            &    R2 \\
\hline
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2 & 84.97 \\
 conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 71.27 \\
 flow\_rate1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 71.9  \\
 flow\_rate1,conc\_nano1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2         & 73.44 \\
 flow\_rate1,conc\_nano1,Kfluid1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 74.25 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2       & 70.58 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 81.67 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,Kfluid2,heat\_flux2,X\_D2             & 40.24 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,heat\_flux2,X\_D2         & 49.33 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,X\_D2             & 72.42 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2       & 74.5  \\
\hline
\end{tabular}
\hline
        \caption{Results of Backward Feature Elimination}
        \label{backward}
    \end{table*}

>>>>

    \begin{table*}
        \centering
        \begin{tabular}{lr}
\hline
 features                                                                                            &    R2 \\
\hline
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2 & 62.49 \\
 conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 68.28 \\
 flow\_rate1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 81.17 \\
 flow\_rate1,conc\_nano1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2         & 71.83 \\
 flow\_rate1,conc\_nano1,Kfluid1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 69.8  \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2       & 64.05 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 88.72 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,Kfluid2,heat\_flux2,X\_D2             & 69.93 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,heat\_flux2,X\_D2         & 46.61 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,X\_D2             & 56.93 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2       & 68.77 \\
 conc\_nano1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2                         & 70.72 \\
 flow\_rate1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2                         & 81.63 \\
 flow\_rate1,conc\_nano1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2                     & 87.88 \\
 flow\_rate1,conc\_nano1,Kfluid1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2                         & 80.33 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2                   & 84.17 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,Kfluid2,heat\_flux2,X\_D2                         & 81.33 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,heat\_flux2,X\_D2                     & 26.72 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,X\_D2                         & 61.71 \\
 flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2                   & 76.7  \\
\hline
\end{tabular}
        \caption{Results of Backward Feature Elimination}
        \label{backward}
    \end{table*}

### 2024-07-22 NN/tables/forward.tex
commit

        \begin{table*}
            \centering
            \begin{tabular}{lr}
\hline
 features                                                            &     R2 \\
\hline
 ['X_D1']                                                            &  14.09 \\
 ['flow_rate2']                                                      &  38.24 \\
 ['conc_nano2']                                                      &  11.24 \\
 ['Kfluid2']                                                         &  62.95 \\
 ['heat_flux2']                                                      &   0.14 \\
 ['flow_rate1', 'Kfluid2']                                           &  63.47 \\
 ['conc_nano1', 'Kfluid2']                                           &  63.88 \\
 ['Kfluid1', 'Kfluid2']                                              &  62.25 \\
 ['heat_flux1', 'Kfluid2']                                           &  77.7  \\
 ['X_D1', 'Kfluid2']                                                 &  76.02 \\
 ['flow_rate2', 'Kfluid2']                                           & -31.69 \\
 ['conc_nano2', 'Kfluid2']                                           &  86.62 \\
 ['heat_flux2', 'Kfluid2']                                           &  76.09 \\
 ['X_D2', 'Kfluid2']                                                 &  78.17 \\
 ['flow_rate1', 'Kfluid2', 'conc_nano2']                             &  76.79 \\
 ['conc_nano1', 'Kfluid2', 'conc_nano2']                             &  87.83 \\
 ['Kfluid1', 'Kfluid2', 'conc_nano2']                                &  88.24 \\
 ['heat_flux1', 'Kfluid2', 'conc_nano2']                             &  91.58 \\
 ['X_D1', 'Kfluid2', 'conc_nano2']                                   &  82.59 \\
 ['flow_rate2', 'Kfluid2', 'conc_nano2']                             &  53.86 \\
 ['heat_flux2', 'Kfluid2', 'conc_nano2']                             &  75.43 \\
 ['X_D2', 'Kfluid2', 'conc_nano2']                                   &  64.89 \\
 ['flow_rate1', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  93.27 \\
 ['conc_nano1', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  76.38 \\
 ['Kfluid1', 'Kfluid2', 'conc_nano2', 'heat_flux1']                  &  92.71 \\
 ['X_D1', 'Kfluid2', 'conc_nano2', 'heat_flux1']                     &  86.97 \\
 ['flow_rate2', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  74.46 \\
 ['heat_flux2', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  81.11 \\
 ['X_D2', 'Kfluid2', 'conc_nano2', 'heat_flux1']                     &  63.44 \\
 ['conc_nano1', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1'] &  83.2  \\
 ['Kfluid1', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1']    &  66.6  \\
 ['X_D1', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1']       &  82.41 \\
 ['flow_rate2', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1'] &  49.69 \\
 ['heat_flux2', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1'] &  61.91 \\
 ['X_D2', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1']       &  70.43 \\
\hline
\end{tabular}
            \caption{Results of Forward Feature Selection for different features}
            \label{table-forward}
        \end{table*}

>>>>

    \begin{table*}
        \centering
        \begin{tabular}{lr}
\hline
 features                                                      &    R2 \\
\hline
 X\_D1                                                         & 15.01 \\
 flow\_rate2                                                   & 34.3  \\
 conc\_nano2                                                   & 10.78 \\
 Kfluid2                                                       & 49.29 \\
 heat\_flux2                                                   & -8.26 \\
 flow\_rate1,Kfluid2                                           & 52.94 \\
 conc\_nano1,Kfluid2                                           & 50.8  \\
 Kfluid1,Kfluid2                                               & 47.57 \\
 heat\_flux1,Kfluid2                                           & 52.31 \\
 X\_D1,Kfluid2                                                 & 62.32 \\
 flow\_rate2,Kfluid2                                           & 29.14 \\
 conc\_nano2,Kfluid2                                           & 61.05 \\
 heat\_flux2,Kfluid2                                           & 66.61 \\
 X\_D2,Kfluid2                                                 & 53.44 \\
 flow\_rate1,Kfluid2,heat\_flux2                               & 60.58 \\
 conc\_nano1,Kfluid2,heat\_flux2                               & 61.96 \\
 Kfluid1,Kfluid2,heat\_flux2                                   & 66.64 \\
 heat\_flux1,Kfluid2,heat\_flux2                               & 42.41 \\
 X\_D1,Kfluid2,heat\_flux2                                     & 66.55 \\
 flow\_rate2,Kfluid2,heat\_flux2                               & 55.24 \\
 conc\_nano2,Kfluid2,heat\_flux2                               & 67.09 \\
 X\_D2,Kfluid2,heat\_flux2                                     & 68.58 \\
 flow\_rate1,Kfluid2,heat\_flux2,X\_D2                         & 90.12 \\
 conc\_nano1,Kfluid2,heat\_flux2,X\_D2                         & 78.64 \\
 Kfluid1,Kfluid2,heat\_flux2,X\_D2                             & 88.23 \\
 heat\_flux1,Kfluid2,heat\_flux2,X\_D2                         & 49.47 \\
 X\_D1,Kfluid2,heat\_flux2,X\_D2                               & 79.9  \\
 flow\_rate2,Kfluid2,heat\_flux2,X\_D2                         & -0.88 \\
 conc\_nano2,Kfluid2,heat\_flux2,X\_D2                         & 63.17 \\
 conc\_nano1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 95.97 \\
 Kfluid1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1                 & 76.54 \\
 heat\_flux1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 60.12 \\
 X\_D1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1                   & 80.67 \\
 flow\_rate2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 68.87 \\
 conc\_nano2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 68.35 \\
 Kfluid1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1     & 80.62 \\
 heat\_flux1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1 & 67.03 \\
 X\_D1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1       & 85.73 \\
 flow\_rate2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1 & 75.7  \\
 conc\_nano2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1 & 78.99 \\
\hline
\end{tabular}
        \caption{Results of Forward Feature Selection for different features}
        \label{forward}
    \end{table*}
